---
title: 'HW4: Bootstrap and Central Limit Theorem'
author: "Scott Payne"
date: "October 23, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
This is a function that takes in data and the number of times you want to sample it and outputs the samples and the means of the samples.
```{r}
b.means <- function(data, num) {
    resamples <- lapply(1:num, function(i) sample(data, replace=T))
    r.means <- sapply(resamples, mean)
    list(resamples=resamples, means=r.means)   
}
```
The following code takes a random sample of n=5 from a normal distribution and uses the bootstrap function to sample it 100 and 1000 times. The histogram of the means of the samples shows that as the number of bootstrap samples increases, the more the histogram of the means resembles a normal distribution.
```{r}
norm5 <- rnorm(5)
b100 <- b.means(norm5, 100)
b1000 <- b.means(norm5, 1000)
hist(norm5)
hist(b100$means)
hist(b1000$means)
```

The following code takes a random sample n=10 from an exponential distribution and uses the bootstrap method to resample the random sample 100 and 1000 times. 
```{r}
exp10 <- rexp(10)
b100 <- b.means(exp10, 100)
b1000 <- b.means(exp10, 1000)
hist(exp10)
hist(b100$means)
hist(b1000$means)
```

#Summary:<br>
The central limit theorem states that the sampling distribution of the mean of any independent, random variable will be normal or nearly normal, if the sample size is large enough. The bootstrap method generates a sampling distribution from a single sample of a population, but the central limit theorem still applies. Even when the population is an exponential distribution, the bootstrap method is able to approximate a normal distribution when the resample size is large enough.
